The Effects of weather on maize yields: New evidence from Kenya

### 2018-12-07 writing/draft3/draft10.tex
writing  and tables..

\color{blue}
\begin{itemize}
\item Add a description of residual and other diagnostic tests (AIC, autocorrelation)
\item Describe the procedure that I have applied to find the preferred way of modelling the  correlation structure in errors (ARMA errors)
\end{itemize}
\color{black}

@@

According to the conditional Lagrange multiplier (LM) test for serial correlation in the idiosyncratic component of the errors (developed by Baltagi \& Li 1991 and Baltagi \& Li 1995), the errors exhibited a within group autcorrelation structure in our models (the p-value of the LM test was $9.48\times10^{-14}$). To investigate the autocorrelation structure of the errors, we estimated several variants of our preferred specification with the autocorrelation structure of a form ARMA($p$,$q$). In particular, we estimated all varieties of our model with ARMA($p$,$q$) errors such that $p\leq2$ and $q\leq2$. Comparing the AIC criteria and using the corresponding likelihood ratio statistics, we found that the most appropriate correlation structure of the errors was ARMA($1$,$1$). The AIC criterion of the model with ARMA($1$,$1$) error structure was $2122.2$ while the AIC criterion of the model without any correlation structure was $2205.1$ and the AIC criterion of the model with ARMA($1$,$0$) errors was $2129.2$. The likelihood ratio test of comparison of

@@

\begin{table}[H]
\caption{\label{ARMA}Comparison of models with different error autcorrelation structure}

\begin{indented}
\lineup
\item[]\begin{tabular}{@{}llll}
\\[-1em]
\br
\\[-1em]
\textbf{Error autocorrelation structure}&\textbf{AIC}&\textbf{Likelihood ratio}&\multicolumn{1}{c}{\textbf{p-value}}\\
\mr
\textit{None}& $2205.1$& & \\
ARMA($1$,$0$)& $2129.2$& $77.9$&$<1\times10^{-4}$ \\
ARMA($0$,$1$)&  $2144.9$& & \\
\rowcolor{Gray}ARMA(${1}$,${1}$)& ${2122.2}$&${24.7}$&${<1\times10^{-4}}$ \\
ARMA($2$,$1$)& $2124.0$&$\00.1$&$\0\00.7066$ \\
ARMA($1$,$2$)&  $2124.2$& & \\
ARMA($2$,$2$)&$2125.8$& $\00.3$&$\0\00.5681$ \\
ARMA($3$,$2$)& $2128.0$& $\00.1$&$\0\00.7312$ \\
ARMA($2$,$3$)&  $2127.6$& & \\
ARMA($3$,$3$)&\multicolumn{3}{c}{\textit{Failed to converge}} \\
\br
\end{tabular}
\end{indented}
\end{table}

>>>>

@@

According to the conditional Lagrange multiplier (LM) test for serial correlation in the idiosyncratic component of the errors (developed by Baltagi \& Li 1991 and Baltagi \& Li 1995), the errors exhibited a within group autcorrelation structure in our models (the p-value of the LM test was $9.48\times10^{-14}$). To investigate the autocorrelation structure of the errors, we estimated several variants of our preferred specification with the autocorrelation structure of a form ARMA($p$,$q$). In particular, we estimated all varieties of our model with ARMA($p$,$q$) errors such that $p\leq2$ and $q\leq2$. Comparing the AIC criteria and using the corresponding likelihood ratio statistics, we found that the most appropriate correlation structure of the errors was ARMA($1$,$1$). The AIC criterion of the model with ARMA($1$,$1$) error structure was $2122.2$ while of the model with ARMA($1$,$0$) errors was $2129.2$. The p-value of the likelihood ratio test of comparison of the with ARMA($1$,$1$) errors and the one with ARMA($1$,$0$) errors was smaller than $1 \times10^{-4}$, hence the ARMA($1$,$1$) errors structure is preferable. The AIC criteria and likelihood ratio test statics of all models with ARMA($p$,$q$) errors can be found in table~\ref{ARMA} in the appendix.

@@

{\begin{center}
\begin{threeparttable}[H]
\caption{\label{ARMA}Comparison of models with different error autcorrelation structure}
\lineup
\begin{indented}

\item[]\begin{tabular}{@{}llll}
\\[-1em]
\br
&&\centre{2}{\textbf{Likelihood ratio} vs. ARMA($1$,$1$)\tnote{a}}\\
\textbf{Error autocorrelation structure}&\textbf{AIC}&\textbf{Statistic}&\multicolumn{1}{l}{\textbf{p-value}}\\
\mr
\textit{None}&$2205.1$&$86.94$&$<1\times10^{-4}$\\
ARMA($1$,$0$)&$2129.2$&$\09.01$&$0.0027$\\
ARMA($0$,$1$)&$2144.9$&${24.72}$&${<1\times10^{-4}}$ \\
\rowcolor{Gray}ARMA(${1}$,${1}$)&${2122.2}$&$---$&$---$\\
ARMA($2$,$1$)&$2124.0$&$\00.14$&$\0\00.7066$\\
ARMA($1$,$2$)& $2124.2$&$\00.01$&$\0\00.9143$\\
ARMA($2$,$2$)&$2125.8$& $\00.31$&$\0\00.8545$\\
\br
\end{tabular}

\end{indented}
\begin{tablenotes}
  \begin{footnotesize}
  \item[a] Likelihood ratio test of comparison with the ARMA(${1}$,${1}$) error structure model. ARMA(${1}$,${1}$) error structure seems to be the most suitable as all lower-order correlation structure models are rejected against ARMA(${1}$,${1}$) while ARMA(${1}$,${1}$) is not rejected against the higher order structures.
\singlespacing
  \end{footnotesize}
\end{tablenotes}
  \end{threeparttable} 
\end{center}
